MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-02-13 MAESTROeX_I/paper.tex
simplifying notation... trying to make algorithm more human-readable

\newcommand{\etarho}{\eta_\rho}
\newcommand{\gammaonebar}{\overline{\Gamma_1}}
\newcommand{\Hnuc}{H_{\rm nuc}}
\newcommand{\omegadot}{\dot\omega}
\newcommand{\pred}{{\rm pred}}
\newcommand{\Sbar}{\overline{S}}

@@

Call {\bf React State}$[ (\rho X_k)^{(2),\star}, (\rho h)^{(2),\star}, p_0^{n+1,\star}]$\\
\phantom{ }\hfill $\rightarrow [ (\rho X_k)^{n+1,\star}, (\rho h)^{n+1,\star}, (\rho \omegadot_k)^{(2),\star}, (\rho \Hnuc)^{(2),\star} ].$

@@

\item First, compute $S^{n+1,\star}$ with
\begin{equation}
S^{n+1,\star} =  -\sigma  \sum_k  \xi_k  (\omegadot_k)^{(2),\star}  + \frac{1}{\rho^{n+1,\star} p_\rho} \sum_k p_{X_k}  ({\omegadot}_k)^{(2),\star} + \sigma \Hnuc^{(2),\star},
\end{equation}
  where $(\omegadot_k)^{(2),\star} = (\rho \omegadot_k)^{(2),\star} /
  \rho^{(2),\star}$ and the thermodynamic quantities are defined using
  $\rho^{n+1,\star}, X_k^{n+1,\star},$ and $T^{n+1,\star}$ as inputs to
  the equation of state.  Then, define
\begin{equation}
 S^{\nph} = \frac{S^n + S^{n+1,\star}}{2},
\end{equation}

@@

Call {\bf React State}$[(\rho X_k)^{(2)},(\rho h)^{(2)}, p_0^{n+1}] \rightarrow [(\rho X_k)^{n+1}, (\rho h)^{n+1}, (\rho \omegadot_k)^{(2)}, (\rho \Hnuc)^{(2)}].$

@@

\begin{enumerate}
\renewcommand{\theenumi}{{\bf \Alph{enumi}}}
\item Define
\begin{equation}
  S^{n+1} =  -\sigma  \sum_k  \xi_k (\omegadot_k)^{(2)}  + \sigma \Hnuc^{(2)} +
  \frac{1}{\rho^{n+1} p_\rho} \sum_k p_{X_k}  ({\omegadot}_k)^{(2)},
\end{equation}
where $(\omegadot_k)^{(2)} = (\rho \omegadot_k)^{(2)} / \rho^{(2)}$
and the thermodynamic quantities are defined using $\rho^{n+1}$,
$X_k^{n+1}$, and $T^{n+1}$ as inputs to the equation of state.

>>>>

\newcommand{\etarho}{\eta_\rho}
\newcommand{\gammaonebar}{\overline{\Gamma}_1}
\newcommand{\Hnuc}{H_{\rm nuc}}
\newcommand{\omegadot}{\dot\omega}
\newcommand{\pred}{{\rm pred}}
\newcommand{\Sbar}{\overline{S}}

@@

Call {\bf React State}$[ (\rho X_k)^{(2),\star}, (\rho h)^{(2),\star}, p_0^{n+1,\star}] 
\rightarrow 
[ (\rho X_k)^{n+1,\star}, (\rho h)^{n+1,\star}, (\rho \omegadot_k)^{n+1,\star}, (\rho \Hnuc)^{n+1,\star} ].$

@@

First, compute $S^{n+1,\star}$ with
\begin{equation}
S^{n+1,\star} =  \left(-\sigma  \sum_k  \xi_k  \omegadot_k  + \frac{1}{\rho p_\rho} \sum_k p_{X_k}  {\omegadot}_k + \sigma \Hnuc\right)^{n+1,\star}.
\end{equation}
  Then, define
\begin{equation}
 S^{\nph} = \frac{S^n + S^{n+1,\star}}{2},
\end{equation}

@@

Call {\bf React State}$[(\rho X_k)^{(2)},(\rho h)^{(2)}, p_0^{n+1}] \rightarrow [(\rho X_k)^{n+1}, (\rho h)^{n+1}, (\rho \omegadot_k)^{n+1}, (\rho \Hnuc)^{n+1}].$

@@

\begin{enumerate}
\renewcommand{\theenumi}{{\bf \Alph{enumi}}}
\item Define
\begin{equation}
  S^{n+1} =  \left(-\sigma  \sum_k  \xi_k \omegadot_k  + \sigma \Hnuc +
  \frac{1}{\rho p_\rho} \sum_k p_{X_k}  \omegadot_k\right)^{n+1}.
\end{equation}
